Fictitious Play in Network Aggregative Games

### 2021-05-05 Documents/FP in NAGs/neurips_2020.tex
Updated NeurIPS
added stylefile

  Note that the NE Condition requires

  \begin{align}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber \\
    & =: \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align}

@@

  \begin{definition}[Upper Semi-Continuous]
    A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.  
  \end{definition}

@@

    This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map

@@

  \begin{theorem}
    There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
    BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
  \end{theorem}

@@

    \begin{equation}
      m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(s) ds \right).
    \end{equation}

@@

    where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m) =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart. We can, therefore, think of the NA game as a network game in which each agent plays the same strategy against each of its neighbours, itself included. As such, any $m$ which satisfies the CTFP property for the equivalent network game also satisfies the CTFP requirement for the network aggregative game.

@@

>>>>

  Note that the NE Condition requires \fb{why?}
%
  \begin{align}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber \\
    & =: \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align}

@@

  \begin{definition}[Upper Semi-Continuous]
    A compact-valued correspondence $\Phi: A \rightarrow B$ is
    \emph{upper semi-continuous} at a point $a$ \fb{domain?} if $g(a)$ \fb{what is $g$?} is non-empty
    and if, for every sequence $a_n \rightarrow a$ and every sequence
    $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a
    convergent subsequence of $(b_n)$ whose limit point $b$ is in
    $g(a)$.
  \end{definition}

  \fb{perhaps we have to introduce some terminology from topology to keep the results self-contained?}

@@

    This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map \fb{why?}

@@

  \begin{theorem}
    There exists a path $m$ which satisfies the property that, for all $\mu$ \fb{remind what this is.}, $m^\mu \in
    BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
  \end{theorem}

@@

   \fb{what is the meaning of the following equation?}
%
    \begin{equation}
      m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(s) ds \right).
    \end{equation}

@@

    where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m)
    =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart \fb{use the reference rather than the name of the author.}. We
    can, therefore, think of the NA game as a network game in which
    each agent plays the same strategy against each of its neighbours,
    itself included. As such, any $m$ which satisfies the CTFP
    property for the equivalent network game also satisfies the CTFP
    requirement for the network aggregative game.

@@

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoNoise.png}
    \caption{\label{fig::Noise10Player}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
    \caption{\label{fig::Noise10Player}}
  \end{figure}
